WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-03-18 lit/sec_3-other-systems.tex
Thesis 4.0

\acrfull{dias} \cite{Kawasaki2018DataReduction} collects and archives data from satellites, weather stations, numerical forecasting models and climate projection models. Once this data is integrated into geographic useful information, DIAS generates results for managing global environmental problems and natural disasters \cite{Kawasaki2018DataReduction}. As mentioned above, \acrshort{dias} has the capability of collecting weather data from multiple data sources which are inherently in different formats. After successfully ingest the data, it generates results which can use for different kind of purposes.

@@

The mechanism of storing data in \acrshort{dias}, similar to the other systems discussed.
These data sets are stored in a larger array system with API software that is used to import the data. APIs work to convert or reformat data into manageable forms and are useful for creating the DIAS storage archive. The API software contains various tools, including the real-time data exploration and archiving system, the data download system, the quality control system and the metadata management system \cite{Kawasaki2018DataReduction}. To store on the large volume of disk space, it converts the data via a provided set of APIs. This can be considered the same as the open data model provided by the \acrshort{fews}. Other than that, \acrshort{dias} consist of additional tools that provide the functionality of quality control of the data, and metadata management which is similar to some of the services in \acrshort{lead}.

As shown in \cref{fi:dias_common_platform}, it offers an application layer that allows scientists in the field to work on research tasks and to develop specific tools and applications by collaborating with experts in information technology \cite{Kawasaki2018DataReduction}. Once the data is achieved on the \acrshort{dias} system, it shares those details via the Shared API layer. Thus it allows users to remote access to the data, and easy integration via the APIs.

@@

\dbc{Both MADIS and netCDF need to cited. Do this at the beginning for each on the systems in this chapter (while they were cited in Chap 1, it's also important to cite them in Chap 2 as well.}
\gkc{Updated.}

@@

\acrshort{madis} contains a distributed architecture for data acquisition, processing and distribution functions.
In addition, the paper mentioned architectural advancement at that time, the various functional hosts have been paired using Linux High Availability (HA) to provide automated failover in the event of a system failure. And it uses following method for data dissemination such as FTP, Local Data Manager (LDM) and the Web OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ArchitectureP2.39}. As mentioned above, the \acrshort{madis} is implemented based on a distributed architecture that is available at the time of its development. Even it is not mentioned, it is using functional calls like Remote Procedure Call (RPC) to invoke among a cluster of nodes. In \cref{fi:madis_flow}, data is transported from the input and preprocessing systems to the central computer systems and then to other hosts for storage and distribution \cite{Macdermaid2005ArchitectureP2.39}. To get high availability, it has added some updates to its architecture as mentioned in the paper. The conclusion of this statement is, these kinds of functionalities are available at the modern the Cloud Computing tools, and out of the box, those tools are providing the scalability and high availability. Using those tools, it possible to implement such a system with less effort and high confidence.

MADIS regularly acquires Mesonet data from dozens of network providers representing more than 14,000 stations. This translates into more than 30,000 station reports every hour. Different systems that work inside and outside the firewall collect the data. This data is sent to the data server of the Advanced Weather-Interactive Processing System (AWIPS) of the central installation for processing and conversion to a common format, NetCDF. NetCDF files are then transferred to MADIS compute nodes \cite{Macdermaid2005ArchitectureP2.39}. This provides an overview of the level of data that \acrshort{madis} handling. This could be a good reference for implementing \acrshort{wdias} and its performance testing. As same as \acrshort{fews}, it is also converting the data into a common format which is \acrshort{netCDF}. Those files are transferred to the compute nodes and allow users to access via OPeNDAP. 
%MADIS computer platforms include Intel-based servers with the Red Hat Enterprise Linux operating system. 
Many of these computers are configured using Linux clustering with high availability \cite{Macdermaid2005ArchitectureP2.39}.% As indicated above, the system heavily depends on the platform. There are some costs involving purchasing their licenses.

As certain MADIS data is considered to be the property of the supplier, access to this data must be checked. To respond to this, MADIS data is divided into six different versions, depending on the access level authorized by the data provider \cite{Macdermaid2005ArchitectureP2.39}. When compared to \acrshort{fews}, \acrshort{madis} provides control based access to the data.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
\label{se:lit_summary}
\db{We presented several related work on WDIA system implementations such as \acrshort{fews}, \acrshort{lead}, \acrshort{dias}, and \acrshort{madis}}. In this research one of major issue that we focused on storing data which are ingested from different sources with different formats efficiently. The \acrshort{fews} and \acrshort{madis} are using the \acrshort{netCDF} as the common data format to store the data which is one of the best solutions available with modern technologies as well. Even it is not mentioned, the \acrshort{dias} and \acrshort{lead} also following a method of having common storage space to store bulk data.
\acrshort{fews} and \acrshort{lead} have the capability of handling the workflow of forecasting, but other systems are mainly focused on providing a weather data management system.
\acrshort{fews} provides a modular approach via its general adapter, and according to the \acrshort{soa} architecture of \acrshort{lead} provides the same functionality via services.
\dbc{Complete highlighted sentence}
\gkc{Updated. Do I need to elaborate more?}

Most of the above systems developed by many developers and researchers, and were developed specifically to address issues like natural disasters. To address use cases such as CUrW, it required to remodel the systems  and define the forecasting flows. Even some of the systems try to follow a generic approach to integrate new modules, it is challenging to deploy modules for a closed source or proprietary software. Further, most of them are depend on the underline platform, and does not support more resource efficient and highly-scalable technologies such as cloud computing.

\dbc{You are making lots of mistakes when using "ing" form of a verb. It seems checking with Grammaly didn't help either.}
\gkc{I fixed all the issues one by one which are shown by Grammarly free version. Can you highlight with a specific example. I'll add more effort to improve.}

>>>>

\acrfull{dias} \cite{Kawasaki2018DataReduction} collects and archives data from satellites, weather stations, numerical forecasting models and climate projection models. Once this data is integrated into geographic useful information, DIAS generates results for managing global environmental problems and natural disasters \cite{Kawasaki2018DataReduction}. \acrshort{dias} has the \hl{capability of collecting} weather data from multiple data sources which are inherently in different formats. \hl{After successfully ingest} the data, it generates results which can use for different kind of purposes.

@@

\hl{The mechanism of storing data in \acrshort{dias}, similar to the other systems discussed.}
These data sets are \hl{stored in a larger array system with API software} that is used to import the data. APIs work to convert or reformat data into manageable forms and are useful for creating the DIAS storage archive. The API software contains various tools, including the real-time data exploration and archiving system, the data download system, the quality control system and the metadata management system \cite{Kawasaki2018DataReduction}. To store on the large volume of disk space, it converts the data via a provided set of APIs. This can be considered the same as the open data model provided by the \acrshort{fews}. Other than that, \acrshort{dias} consist of additional tools that provide the functionality of quality control of the data, and metadata management which is similar to some of the services in \acrshort{lead}.

As shown in \cref{fi:dias_common_platform}, it offers an application layer that allows scientists %in the field 
to work on research tasks and to develop specific tools and applications by collaborating with IT experts \cite{Kawasaki2018DataReduction}. Once the data is achieved on the \acrshort{dias} system, it shares those details via the Shared API layer. \hl{Thus it} allows users to remote access to the data, and easy integration via the APIs.

@@

@@

\acrshort{madis} contains a distributed architecture for data acquisition, processing and distribution functions.
In addition, \hl{the paper mentioned architectural advancement at that time,} the various functional hosts have been paired using Linux High Availability (HA) to provide automated failover in the event of a system failure. It uses several methods for data dissemination such as FTP, Local Data Manager (LDM) and the Web OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ArchitectureP2.39}. %As mentioned above, the \acrshort{madis} is implemented based on a distributed architecture that is available at the time of its development. Even it is not mentioned, it is 
It users functional calls like Remote Procedure Call (RPC) to invoke among a cluster of nodes. In \cref{fi:madis_flow}, data is transported from the input and preprocessing systems to the central computer systems and then to other hosts for storage and distribution \cite{Macdermaid2005ArchitectureP2.39}. To get high availability, it has added some updates to its architecture as mentioned in the paper. The conclusion of this statement is, these kinds of functionalities are available at the modern the Cloud Computing tools, and out of the box, those tools are providing the scalability and high availability. Using those tools, it possible to implement such a system with less effort and high confidence.

MADIS regularly acquires Mesonet data from dozens of network providers representing more than 14,000 stations. This translates into more than 30,000 station reports every hour. Different systems that work inside and outside the firewall collect the data. This data is sent to the data server of the Advanced Weather-Interactive Processing System (AWIPS) of the central installation for processing and conversion to a common format, NetCDF. NetCDF files are then transferred to MADIS compute nodes \cite{Macdermaid2005ArchitectureP2.39}. %This provides an overview of the level of data that \acrshort{madis} handling. 
This could be a good reference for implementing \acrshort{wdias} and its performance testing. As same as \acrshort{fews}, it is also \hl{converting} the data into %a common format which is 
\acrshort{netCDF}. Those files are transferred to the compute nodes and accessible via OPeNDAP. 
%MADIS computer platforms include Intel-based servers with the Red Hat Enterprise Linux operating system. 
Many of these computers are configured using Linux clustering with high availability \cite{Macdermaid2005ArchitectureP2.39}.% As indicated above, the system heavily depends on the platform. There are some costs involving purchasing their licenses.

As certain MADIS data is considered to be the property of the supplier, access to this data must be checked. To respond to this, MADIS data is divided into six different versions, depending on the access level authorized by the data provider \cite{Macdermaid2005ArchitectureP2.39}. When compared to \acrshort{fews}, \acrshort{madis} provides control-based access to the data.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
\label{se:lit_summary}
We presented several related work on WDIA system implementations such as \acrshort{fews}, \acrshort{lead}, \acrshort{dias}, and \acrshort{madis}. In this research one of major issue that we focused on is storing data ingested from different sources with different formats efficiently. The \acrshort{fews} and \acrshort{madis} are using the \acrshort{netCDF} as the common data format to store the data which is one of the best solutions available with modern technologies as well. Even it is not mentioned, the \acrshort{dias} and \acrshort{lead} also following a method of having common storage space to store bulk data.
\acrshort{fews} and \acrshort{lead} have the capability of handling the workflow of forecasting, but other systems are mainly focused on providing a weather data management system.
\acrshort{fews} provides a modular approach via its general adapter, and according to the \acrshort{soa} architecture of \acrshort{lead} provides the same functionality via services.

Most of the \hl{above systems developed} by many researchers, and were developed specifically to address issues like natural disasters. To address use cases such as CUrW, \hl{it required} to remodel the systems  and define the forecasting flows. Even some of the systems try to follow a generic approach to integrate new modules, it is challenging to deploy modules for a closed source or proprietary software. Further, most of them \hl{are depend} on the underline platform, and does not support more resource efficient and highly-scalable technologies such as cloud computing.

### 2020-03-18 method/sec_0_introduction.tex
Thesis 4.0

This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}.
\cref{se:high_level_design} includes a brief discussion on how the weather forecasting is happening and why it needs to interact with multiple data formats is presented.
\cref{se:architectural_decisions} discussed about how did we evolve over the architectural design while designing and implementing the \acrshort{wdias}.
\cref{se:microservice} gives a better understanding of the microservice architectural concepts that follow while implementing the \acrshort{wdias}.
Then the reasons behind developing \acrshort{wdias} database structure and technologies use for that discussed in \cref{se:db_struct}.
\cref{se:data_preprocess} discussed how the \acrshort{wdias} enables for data preprocessing and adding capabilities via the concept of Extensions.
Final \cref{se:query} includes details on how to perform timeseries search and Geo-based queries on the \acrshort{wdias}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{High-level Design}
\label{se:high_level_design}

To get an overall idea of the flow of weather prediction, let us look into one of the flows using at \acrshort{curw} \cite{CUrWSL2017SL}.
\dbc{Use CUrW-SL}
\gkc{FIXED}

\begin{enumerate}
    \item Extract \acrshort{GRIB} \acrshort{wrf} model data to \acrshort{netCDF}
    \item From \acrshort{netCDF} to \acrshort{csv} of each location data, then feed to HEC-HMS hydro-dynamic model and get the output as \acrshort{csv}
    \item \acrshort{csv} and Rain cell Grid feed into the FLO2D hydro-logic model, and get the water level as ASCII Grid files after completion of simulation
    \item Upload ASCII files to ArcGIS create Raster files, then use for the LOSS Estimation
\end{enumerate}
When looked into the above flow, it gives a clear understanding of multiple data formats using while weather predictions.
Other than that, to correct the model outputs, it required to collect real-time data such as;
\begin{itemize}
    \item Automated weather station sending data in higher frequent intervals via HTTP protocol
    \item Automated water level stations send data in higher frequency
\end{itemize}
Other than above many data formats using for handling data based on devices and standards which are using. Also, for data modeling, it needs to convert the data into model compatible data format, then after successfully run the model it needs to collect data from the model output data formats.

@@

\cref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system which consists of the following modules:

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\textwidth]{method/misc/weather_data_system_components.jpg}}
\caption{Modules of a weather data system.}
\label{fi:wdia_components}
\end{figure}

@@

\dbc{Why are you referring to timeseries here? It's not one of the 3 key components in Fig. 3.1.}
\gkc{Move this to WDIAS microservices \cref{sebse:wdias_microservices}. It need to describe the reason behind decompose into microservices. Seems to be this is confusing at this point.}

@@

% \subsubsection{Base of WDIAS architecture}
\dbc{What's Base of WDIAS architecture?}
\gkc{Moved to WDIAS database structure section \cref{sebse:wdias_microservices}}

% \hl{The base of WDIAS architecture origins based on attributes of a timeseries.} There are many attributes to differentiate timeseries one from another. But 
% Among many attribute to differentiate a timeseries from another, the following can be consider as the key attributes in uniquely identify a timeseries from another: % for the \acrshort{wdias}.
\dbc{Highlighted sentence doesn't make sense to me. All yellow highlights mean they are not clear.}

>>>>

This chapter presents the design decisions taken while implementing \acrfull{wdias}, and how is the system got \hl{adapted from the systems analyzed in Chapter} \ref{ch:literature}.
\cref{se:high_level_design} presents a brief discussion on how the weather forecasting is happening and why it needs to interact with multiple data formats.
\cref{se:architectural_decisions} presents how the architectural design of proposed solution evolved while designing and implementing \acrshort{wdias}.
\cref{se:microservice} presents %gives a better understanding of the 
microservice architectural concepts followed while implementing \acrshort{wdias}.
Then the reasons behind developing \acrshort{wdias} database structure and technologies used are discussed in \cref{se:db_struct}.
\cref{se:data_preprocess} discusses how \acrshort{wdias} enables data preprocessing and adding capabilities using extensions.
Finally, \cref{se:query} includes details on how to perform timeseries search and geo-based queries on the \acrshort{wdias}.

\dbc{It's just WDIAS. "the" should be used only on essential places to being the meaning. }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{High-level Design}
\label{se:high_level_design}

To get an overall idea of the flow of weather prediction, let us look into one of the \hl{flows using} at the \acrshort{curw} \cite{CUrWSL2017SL}.

\begin{enumerate}
    \item Extract \acrshort{GRIB} \acrshort{wrf} model data to \acrshort{netCDF}
    \item \hl{From} \acrshort{netCDF} to \acrshort{csv} of each location data, then feed to HEC-HMS hydro-dynamic model and get the output as a \acrshort{csv} file.
    \item \acrshort{csv} and \hl{Rain cell Grid feed} into the FLO2D hydrologic model, and get the water level as ASCII Grid files after the simulation is complete.
    \item Upload ASCII files to \hl{ArcGIS create raster files, then use for the LOSS Estimation}
\end{enumerate}

\hl{When looked into the above flow, it gives a clear understanding of multiple data formats using while weather predictions.}
Also, to correct the model outputs, \hl{it required} to collect real-time data such as:
\begin{itemize}
    \item Frequently collected automated weather station data via HTTP protocol
    \item Frequently collected automated water level stations data
\end{itemize}

\hl{Other than above many data formats using for handling data based on devices and standards which are using.} Also, for data modeling, it needs to convert the data \hl{into model compatible data format}. Then \hl{after successfully run the model it needs to collect data from the model output data formats.}

@@

\cref{fi:wdia_components} shows the basic functions of a weather data integration and assimilation system consisting of the following modules:

\begin{figure}[htbp]
\centerline{\includegraphics[width=1\textwidth]{method/misc/weather_data_system_components.jpg}}
\caption{Modules of a weather data system.}
\label{fi:wdia_components}
\end{figure}

@@

@@

% \subsubsection{Base of WDIAS architecture}
% \hl{The base of WDIAS architecture origins based on attributes of a timeseries.} There are many attributes to differentiate timeseries one from another. But 
% Among many attribute to differentiate a timeseries from another, the following can be consider as the key attributes in uniquely identify a timeseries from another: % for the \acrshort{wdias}.

### 2020-03-18 method/sec_1-architectural_decisions.tex
Updates from Overleaf
Thesis 4.0

The initial design of \acrshort{wdias} used the \acrfull{soa}. Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} is acting as a common layer for all of the modules. By default, \acrshort{esb} also provides publisher/subscribe (pub/sub) capabilities.
\hl{Because} \acrshort{esb} \hl{mediators can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
\gkc{FIXED below}
The \acrshort{esb} has the processing units called \emph{mediators}. A mediator can take a message, carry out some predefined actions on it, and output the modified message. These mediator capabilities can use to integrate the modules of a weather data system as shown in \cref{fi:wdia_components}. \acrshort{esb} also supports different transportation protocols such as HTTP and Web sockets. However, it turned out that \acrshort{esb} is not suitable for data streaming or bulk data processing. Also, \acrshort{esb} suffers from a single point of failure, as all the messages are going through a common bus and slower communication (cant use for transfer data).

@@

\dbc{Kubernetes is a product. What you need to refer is to the concept of container-orchestration. Fix.}

@@

\dbc{What are these 2 bullets?}
\gkc{Absorbed those two points into above paragraph}
\dbc{Don't use shortened words like it's, isn't, don't,... in writing}

>>>>

The initial design of \acrshort{wdias} used the \acrfull{soa}. Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} could act as a \hl{common layer} for all of the modules. By default, \acrshort{esb} also provides publisher/subscribe (pub/sub) capabilities.
\hl{Because \acrshort{esb} mediators can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
\dbc{Last sentence incomplete too.}

The \acrshort{esb} has the processing units called \emph{mediators}. A mediator can take a message, carry out some predefined actions on it, and output the modified message. These mediator capabilities can use to integrate the modules of a weather data system as shown in \cref{fi:wdia_components}. \acrshort{esb} also supports different transportation protocols such as HTTP and Web sockets. However, it turned out that \acrshort{esb} is not suitable for data streaming or bulk data processing. Also, \acrshort{esb} suffers from a single point of failure, as all the messages are going through a common bus and slower communication (cant use for transfer data).

@@

@@

### 2020-03-18 method/sec_3-microservice.tex
Don't use shortened words like it's, isn't, don't,... in writing
Thesis 4.0

% \hl{Among the characteristics of microservice, a few characteristics heavily affect while moving from} \acrshort{soa} to microservice.
\dbc{M in Microservice should be capitalized only on begining of a sentence.}

There are lots of microservice patterns developed and evolved. Throughout the following sections, we will discuss in brief some of the microservice design patterns mostly used in the context of designing \acrshort{wdias} architecture. Next, we will discuss how microservice architecture promote to only to create endpoints which only belong to each service logical domain. Next, discuss only using database per service which allows to loosely couple between systems and achieves high scalability. In Sagas, we discuss how distributed transactions can achieve over microservices. Next, we will discuss a concept called \emph{the scale cube}, which explains the scalability from the perspective of x,y, and z-axis.

@@

Even \acrshort{wdias} is a design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scaling the system further. This will be more discussion in \cref{se:discussion}.

>>>>

% \hl{Among the characteristics of microservice, a few characteristics heavily affect while moving from} \acrshort{soa} to microservice.
There are lots of microservice patterns developed and evolved. Throughout the following sections, we will discuss in brief some of the microservice design patterns mostly used in the context of designing \acrshort{wdias} architecture. Next, we will discuss how microservice architecture promote to only to create endpoints which only belong to each service logical domain. Next, discuss only using database per service which allows to loosely couple between systems and achieves high scalability. In Sagas, we discuss how distributed transactions can achieve over microservices. Next, we will discuss a concept called \emph{the scale cube}, which explains the scalability from the perspective of x,y, and z-axis.

@@

Even \acrshort{wdias} is a design based on the Y-axis scaling, it is possible to use the Z-axis scaling to scaling the system further. This will be more discussion in \cref{se:discussion}.
